Deciding to Disclose

### 2015-09-14 Model.tex
scenarios - contexts
clarify that we mean ‘decisions’ by same outputs

Typically in the UK, women have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care. In the UK, and unlike most healthcare scenarios, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

>>>>

Typically in the UK, women have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care. In the UK, and unlike most healthcare contexts, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

### 2015-09-14 agent_models.tex
scenarios - contexts
clarify that we mean ‘decisions’ by same outputs

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

>>>>

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.
